The Calculus of Linear Constructions

### 2021-10-19 writing/lics22/lics22.tex
lics22

  \subsubsection{Backwards Capability}
  To show that CLC is backwards compatible with CC$\omega$, we construct a function that annotates CC$\omega$ terms with sort $U$, lifting them into the non-linear fragment of CLC.

>>>>

  \subsubsection{Backwards Compatibility}
  To show that CLC is backwards compatible with CC$\omega$, we construct a function that annotates CC$\omega$ terms with sort $U$, lifting them into the non-linear fragment of CLC.
